---
title: "Lecture 5"
author: "Viktor"
date: '2020-03-02'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
#install.packages("tidyverse")
```

```{r}
library(tidyverse)
library(broom)
```

T1: Using the diabetes data, convert variables height and weight to metric system and re-create the below plot (hint: facetting rows and columns requires to wrap the variable names in vars())

~ try to avoid when using facet_wrap. Use facet_wrap(vars(...))

```{r}
diabetes2_5 <- diabetes2 %>%
  mutate(height = height * 2.54, weight = weight * 0.45359237)
  
diabetes2_5 %>% 
  ggplot(mapping = aes(x = height, y = weight))+
  geom_point()+
  geom_smooth(method = lm)+
  facet_grid(gender ~ location)
  #facet_wrap(vars(location, gender))
```

T2: Create the below nested tibble

Group location and gender, peform lm on each group

```{r}
groupLG = diabetes2_5 %>% 
  group_by(location,gender) %>% 
  nest()
```

```{r}
H_W_model <- function(df){
  lm(weight ~ height, data = df)
}
```


```{r}
groupLG <- groupLG %>% 
  mutate(model = map(data, H_W_model))
groupLG
```


T3: Create the below nested tibble


```{r}
glance <- groupLG %>% 
  mutate(glance = map(model, broom::glance))  %>% 
  unnest(glance)

glance
```

T4: Create the below nested tibble

```{r}
tidy <- groupLG %>% 
  mutate(tidy = map(model, broom::tidy))  %>% 
  unnest(tidy)

tidy
```


T5: Create the below nested tibble

```{r}
#tidy <- groupLG %>% 
#  mutate(tidy = map(model, broom::tidy))  %>% 
#  unnest(tidy)

tidy_conf <- tidy %>% 
  mutate(tidy_conf = map(model, broom::confint_tidy)) %>% 
  unnest(tidy_conf)

tidy_conf
```


T6: Re-create the coefficient plot from David Robinson’s talk at the 2016 New York R Conference (look at slides for answer)


```{r}
tidy_conf %>%
  filter(term == "height", conf.low > 0) %>% 
  select(location, gender, estimate, conf.low, conf.high) 
```



```{r}

plotten <- tidy_conf %>% 
  filter(term == "height", conf.low > 0) %>% 
  select(location, gender, estimate, conf.low, conf.high)

plotten <- plotten %>% 
  mutate(location_gender = paste(location, gender,sep= "_"))

plotten
```


```{r}
ggplot(data = plotten, mapping = aes(x = estimate, y = location_gender))+
  geom_point()+
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high, height = 0.2))+
  ggtitle("Estimated increase in weight per 1 cm gain in height")+
  ylab("") 
# labs(y = ..., title = ...)

# theme_bw() 
```

