---
title: "NotesLecture2"
author: "Viktor"
date: '2020-02-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Basics from lexture 1
## R Markdown
```{r}
a <- c(2,3)
b<- c("sdf", "sase")
c<- c(TRUE,FALSE)
str(a)
str(b)
str(c)
```

violine plots - modality of the data 
boxplots
y-axis should start at 0
remove reduntant information

No 0-indexing in R




```{r}
install.packages("tidyverse")
install.packages("devtools")
library("devtools")
install_github("ramhiser/datamicroarray")
```


```{r}
library("tidyverse")
library("datamicroarray")
```

```{r}
data('gravier', package = 'datamicroarray')
set.seed(676571)
cancer_data=mutate(as_tibble(pluck(gravier,"x")),y=pluck(gravier,"y"),pt_id=1:length(pluck(gravier, "y")),age=round(rnorm(length(pluck(gravier,"y")),mean=55,sd=10),1))
cancer_data=rename(cancer_data,event_label=y)
cancer_data$age_group=cut(cancer_data$age,breaks=seq(10,100,by=10))
```

```{r}
select(slice(cancer_data,1:8),pt_id,age,age_group,event_label,1:5)
```


Q1: What is this data?

cancer_data

Q2: How many rows and columns are there in the data set in total?

```{r}
ncol(cancer_data)
nrow(cancer_data)
dim(cancer_data)
```
Q3: Which are the variables and which are the observations in relation to rows and columns?
C - variables
R- observations
(tidy data)

T2: linegraph
  geom_line()

T3: boxplot of one variable

```{r}
ggplot(data = cancer_data,
       mapping = aes(x = "my_gene", y = g1A01)) +
  geom_boxplot()

# x needs to be specified
```

T4: histogram of one variable

```{r}
ggplot(data = cancer_data, aes(x = age)) +
  geom_histogram()

# 30 is standard. can be changed
```


T5: densitogram of one variable

```{r}
ggplot(data = cancer_data, aes(x = age)) +
  geom_density() # adjust = 0.5 (parameter) how precise the curve fits the data
```
Q4: Do all geoms require both x and y?
No, geom_histogram() and geom_density() does not.


T6: Pick your favourite gene and create a boxplot of expression levels stratified on the variable event_label

```{r}
ggplot(data = cancer_data,
       mapping = aes(x = event_label, y = g2E09)) +
  geom_boxplot()

# stratisfied into good and poor responses, x = event_label
```

T7: Like T6, but with densitograms

```{r}
ggplot(data = cancer_data, aes(x = g2E09, group = event_label)) +
  #above global mapping, as much as possible should be specified here. applies to everything below
  # group generates a non colored stratification
  geom_density()

# fill parameter (instead of group), fill = event_label 

```

T8: Pick your favourite gene and create a boxplot of expression levels stratified on the variable age_group

```{r}
ggplot(data = cancer_data,
       mapping = aes(x = age_group, y = g2E09, fill = event_label, )) +
  geom_boxplot(alpha = 0.5)

# data is stratified with event_label
# labs() is good for labeling the plot. Can include different kinds of labels. 

```


T9: Pick your favourite gene and create a scatter-plot of expression levels versus age


```{r}
ggplot(data = cancer_data,
       mapping = aes(x = age, y = g2E09, fill = event_label)) +
  ggtitle("gene vs age") +
  geom_point(alpha = 1) +
  geom_smooth()

```

T10: Pick your favourite two genes and create a scatter-plot of their expression levels

```{r}
ggplot(data = cancer_data,
       mapping = aes(x = g2E10, y = g2E09, fill = event_label)) +
  ggtitle("gene vs age") +
  geom_point(alpha = 0.5) +
  geom_smooth() +
  facet_grid(age_group ~ .) +
  scale_fill_discrete(name = "Good or Bad")
  
```

T11: Recreate the following plot

```{r}
ggplot(data = cancer_data,
       mapping = aes(x = event_label, y = g2E09, fill = event_label)) +
  geom_boxplot(alpha=0.5) +
  coord_flip() +
  theme(legend.position = "none") +
  labs(title = "A prognostic DNA ...", subtitle = "Labeling: ....") +
  xlab("Event After Diagnosis") +
  ylab("Expression level of ...")
  
```

Q5: Using your biological knowledge, what is your interpretation of the plot?

T12: Recreate the following plot

```{r}
ggplot(data = cancer_data,
       mapping = aes(x = age, y = g2E09)) +
  
  geom_point(aes(color = event_label),shape = 21) +
  
  geom_smooth(aes(color = event_label), method='lm', se = FALSE)  +
  scale_fill_discrete(name = "Label") +
  
  labs(title = "A prognostic DNA ...",
       subtitle = "Labeling: ....", 
       x = "Subject age", 
       y = "Expression level") 

```

